\documentclass[12pt]{article}

\usepackage{geometry}
\geometry{letterpaper, portrait}

\usepackage{enumitem}

\def\threedigits#1{%
	\ifnum#1<100 0\fi
	\ifnum#1<10 0\fi
	\number#1}

\title{Autonomous Sailboat Message Format}
\author{Thomas Gwynne-Timothy}

\begin{document}

\section*{Overview}

The sailboat supports remote control and data logging via XBee radio. When configured correctly, the XBee radios provides a serial interface for transmitting and receiving. This document describes the message format supported by the sailboat.

\section*{Messages}

The radio interface uses an NMEA-style message format. This format uses a header and a checksum footer. The data fields are comma-delimited. The first data field is a three-digit number that indicates the message type. The following fields hold the data specific to the type. The generic message format is shown below.

\begin{center}
	\texttt{\$DALSAIL,<type>,<arg1>,...,<argn>*checksum\textbackslash r\textbackslash n}
\end{center}

\noindent 
There are currently 11 different message types. They are listed below with their respective type numbers:

\begin{enumerate}[label={\textbf{\protect\threedigits{\theenumi}}}, start=0, leftmargin=0.4\linewidth]
	\setlength\itemsep{0.1em}
	\item Message acknowledgment
	\item Mode change
	\item State change
	\item Remote motor control
	\item Way point entry
	\item Data log configuration
	\item GPS data log
	\item Wind vane data log
	\item Compass data log
	\item Navigation status log
	\item System reset cause
\end{enumerate}

\noindent
The arguments for each type of message are described below.

\subsection*{\textbf{000} Message Acknowledgment}

These messages are sent from the sailboat to acknowledge that it has received and handled commands sent to it. There is a single argument that indicates the acknowledgment status. The statuses are listed below.

\begin{enumerate}[label={\textbf{\protect\threedigits{\theenumi}}}, start=0, leftmargin=0.4\linewidth]
	\setlength\itemsep{0.1em}
	\item 
\end{enumerate}

\subsection*{\textbf{001} Mode Change}

\subsection*{\textbf{002} State Change}

\subsection*{\textbf{003} Remote Motor Control}

\subsection*{\textbf{004} Way Point Entry}

\subsection*{\textbf{005} Data Logging Configuration}

\subsection*{\textbf{006} GPS Data Log}

\subsection*{\textbf{007} Wind Vane Data Log}

\subsection*{\textbf{008} Compass Data Log}

\subsection*{\textbf{009} Navigation Status Log}

\subsection*{\textbf{010} System Reset Cause}

\section*{Usage}

\end{document}
